An open source scientific article

### 2022-10-12 src/tex/ms.tex
Added prelimiary vlos cdf
Added catalog histograms

@@

\begin{figure*}
    \script{cmc_single_clusters.py}
    \gridline{
        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.0002.pdf}{0.49\textwidth}{}
        \fig{figures/cmc_single_clusters_vout-N4e5-rv0.5-rg8-Z0.0002.pdf}{0.49\textwidth}{}
    }
    \gridline{
        \fig{figures/cmc_single_clusters_vout-N8e5-rv2-rg8-Z0.0002.pdf}{0.49\textwidth}{}
        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.02.pdf}{0.49\textwidth}{}
    }
    \caption{
        Scatter plots of the cluster ejection velocity $V_{rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample CMC models (see the beginning of \S\ref{subsec:single_clusters} for details).
        The histograms show the same data in 1D.
        The different types of encounters are color-coded: encounters between a binary star and a CO are in red,
        encounters between a mixed binary (1 star and 1 CO) and a CO are in blue, encounters between a mixed binary and a star are in yellow, and encounters between a CO binary and a star are in purple.
        The $N$-body core radius $r_{c, NB}$ \citep{1985ApJ...298...80C} of the model is plotted in maroon over the timewise histogram.
    }
    \label{fig:cmc_single_clusters}
\end{figure*}

>>>>

% My commands
\newcommand{\CMC}{\texttt{CMC}}
\newcommand{\CMCcat}{\texttt{CMC Cluster Catalog}}
\newcommand{\fewbody}{\texttt{Fewbody}}

@@

\begin{figure*}
    \script{cmc_single_clusters.py}
    \gridline{
        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.0002.pdf}{0.49\textwidth}{}
        \fig{figures/cmc_single_clusters_vout-N4e5-rv0.5-rg8-Z0.0002.pdf}{0.49\textwidth}{}
    }
    \gridline{
        \fig{figures/cmc_single_clusters_vout-N8e5-rv2-rg8-Z0.0002.pdf}{0.49\textwidth}{}
        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.02.pdf}{0.49\textwidth}{}
    }
    \caption{
        Scatter plots of the cluster ejection velocity $V_{rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample \CMC\ models (see the beginning of \S\ref{subsec:single_clusters} for details).
        The histograms show the same data in 1D.
        The different types of encounters are color-coded: encounters between a binary star and a CO are in red,
        encounters between a mixed binary (1 star and 1 CO) and a CO are in blue, encounters between a mixed binary and a star are in yellow, and encounters between a CO binary and a star are in purple.
        The $N$-body core radius $r_{c, NB}$ \citep{1985ApJ...298...80C} of the model is plotted in maroon over the timewise histogram.
    }
    \label{fig:cmc_single_clusters}
\end{figure*}

\begin{figure}[ht!]
    \script{cmc_orbits_cdf.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cmc_orbits_cdf_S.pdf}
        \caption{
            Plot showing orbit cdf.
        }
        \label{fig:cmc_orbits_cdf}
    \end{centering}
\end{figure}

\begin{figure*}
    \script{cmc_catalog.py}
    \centering
    \includegraphics[width=\textwidth]{figures/cmc_catalog_S.pdf}
    \caption{
        Histograms for all MS stars ejected from the \CMCcat\ models as a result of BSCO encounters.
        The three columns display the cluster ejection velocities $v_{\rm out}$, the present-day straight-line travel distances $d$, and the masses $m$ of the ejected objects, respectively.
        Each row divides the data across the values for the \CMC\ model parameters size $N$ (number of objects), initial virial radius $r_{\rm vir}$ (parsecs), or metallicity $Z$.
        Each histogram is averaged over all models computed with the respective model parameter.
        In the right column (the mass plots), the data are further divided by whether the ejection occurred before or after the BH-ejection core collapse of the cluster, if one occurred within the integration time.
    }
    \label{fig:cmc_catalog}
\end{figure*}
